\documentclass[11pt]{article}
\setlength{\textheight}{9truein}
\setlength{\topmargin}{-0.9truein}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}
\setlength{\columnsep}{.4in}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\renewcommand{\abstractname}{Abstract}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{url}

\title{Machine Learning Practise\\Playground Series - Season 3, Episode 9}
\author{Ben Colquhoun}
\date{7/3/23}
\begin{document}
\pagestyle{plain}
\maketitle
\section*{Outline of the Problem}
The task here is to predict the strength of concrete, given an instance of the concrete. This task was found as a Kaggle competition -"Playground Series - Season 3, Episode 9", joined 7 days into the 2 week duration. 
\section*{Exploratory Data Analysis}
\subsection*{Initial Features}
Inital investigation of the data provided the following features from the the training set, with expanded explanations with reference to a Kaggle discussion of Phong Nyugen \cite{feature_descriptions}. 
\begin{itemize}
  \item id
  \begin{itemize}
    \item Id of the instance
    \item Integer
    \item Unimportant feature for comparing strength of concrete
  \end{itemize}
  \item CementComponent
  \begin{itemize}
    \item Amount of cement added to concrete 
    \item Float
    \item More cement improves strength of the concrete, though too much may cause it to be brittle. Important feature. 
  \end{itemize}
  \item BlastFurnaceSlag
  \begin{itemize}
    \item Amount of slag added to concrete 
    \item Float
    \item Slag can be used as a cement substitute in creating concrete. Important feature. 
  \end{itemize}
  \item FlyAshComponent
  \begin{itemize}
    \item Amount of fly ash added to concrete 
    \item Float
    \item Fly ash can be used as a cement substitute in creating concrete. Important feature.
  \end{itemize}
  \item WaterComponent
  \begin{itemize}
    \item Amount of water added to concrete 
    \item Float
    \item Water is the binding agent of the other components. Important feature. 
  \end{itemize}
  \item SuperplasticizerComponent
  \begin{itemize}
    \item Amount of superplasticizer added to concrete 
    \item Float
    \item Chemical additive to improve workability without changing water content. Reasonably important feature. 
  \end{itemize}
  \item CoarseAggregateComponent
  \begin{itemize}
    \item Amount of coarse aggregate added to concrete 
    \item Float
    \item Gravel/crushed stone added to cement for structure. Reasonably important feature. 
  \end{itemize}
  \item FineAggregateComponent
  \begin{itemize}
    \item Amount of fine aggregate added to concrete 
    \item Float
    \item Sand added to cement for structure. Reasonably important feature. 
  \end{itemize}
  \item AgeInDays
  \begin{itemize}
    \item Days since concrete poured 
    \item Integer
    \item Longer drying times increases the strength up to a point dependant on other factors. Important feature when combined with other factors. 
  \end{itemize}
\end{itemize}

\begin{thebibliography}{9}
  \bibitem{feature_descriptions}
  Nyugen, P. (2023, March). \textit{Detailed feature description and feature engineering by ChatGPT}. 
  Retrieved March 7, 2023, 
  from \url{https://www.kaggle.com/competitions/playground-series-s3e9/discussion/391066}

\end{thebibliography}

\end{document}